---
title: "Reproducibility of Centiloids"
author: "UCSF; version 2.05"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r cohort, include=FALSE}

#INPUT 1: Please provide the full path to comma-separated .csv file with the Amyloid PET biomarkers and demographics/cognitive/genetic data in the following format:'/Users/user/projects/cohort_centiloids.csv'. Please note the variables in the spreadsheet MUST BE named according to the example provided in demo. 

###NOTE: if you re-run analysis please provide the full path to the '*_prepared_dataset_*.csv' generated with the previous run.

filename='demo/demo_data.csv' # run demo cohort as example

#INPUT 2: Please provide cohort's label in the following format: e.g., 'IDEAS'
cohort='Demo' # run demo cohort as example

#Once the information provided here click 'Save' and then 'Knit'. If any problems with knitting, please try Run All first and then Knit.

```

# Cohort: `r cohort`

```{r setup, include=FALSE,  echo=F, message=FALSE, results='hide'}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
source("code/load_libraries.R")
source("code/prep_baseline_data.R")

# Check if the provided .csv exists
if (file.exists(filename)) {
  dataset<-read.csv(filename, sep=",", na.strings=c("","n/a","NA","NaN","na"))
} else {
 stop("Provided .csv does not exist.")
}

# Check that minimal set of required variables exist
required_columns <- c("id", "cl", "tracer", "male", "age") # additional but not required columns: "dx", "mmse", "cdr", "apoe", "visual_read"
missing_columns <- setdiff(required_columns, names(dataset))
if (length(missing_columns) > 0) {
  stop("The following required columns are missing:", paste(missing_columns, collapse = ", "), "\n")
}

# If this is the first time processing the cohort, format the dataset to a specific format
if (grepl('prepared_dataset', filename)==F) {
  dataset<-prep_baseline_data(dataset)
  
  #save prepared dataset for future reference; do not share this output file [contains individual data].
  write.csv(dataset,paste0(cohort,'_prepared_dataset_',format(Sys.Date(), "%Y-%m-%d"), ".csv"))
}
```

## Chapter I: Gaussian Mixture Models

#### Optimal number of components in GMM [1-5]

```{r gaussian mixure models optimal number of k, echo=FALSE, message=FALSE, warning=FALSE, results='hide', include=FALSE}
# load required functions
source("code/gmm_bic_criteria.R")
source("code/gmm_aic_criteria.R")
source("code/gmm_silhouette_criteria.R")
source("code/gmm_icl_criteria.R")
source("code/gmm_loglik_criteria.R")

# examine various metrices to define best number of components in the dataset
best_k_aic <- find_best_gmm_aic(dataset)
best_k_loglik <- find_best_gmm_loglik(dataset)
best_k_bic <- find_best_gmm_bic(dataset)
best_k_sil <- find_best_gmm_silhouette(dataset)
best_k_icl <- find_best_gmm_icl(dataset)

# print the resulting table highlighting in bold the best fit
k_selection <- t(data.frame(round(best_k_aic$aic_values,2),
                            round(best_k_loglik$loglik_values,2),
                          round(best_k_bic$bic_values,2),
                          round(best_k_sil$silhouette_scores,2),
                          round(best_k_icl$icl_values,2)))

k_selection[1,best_k_aic$best_k]<-cell_spec(k_selection[1,best_k_aic$best_k], bold = T)
k_selection[2,best_k_loglik$best_k]<-cell_spec(k_selection[2,best_k_loglik$best_k], bold = T)
k_selection[3,best_k_bic$best_k]<-cell_spec(k_selection[3,best_k_bic$best_k], bold = T)
k_selection[4,best_k_sil$best_k]<-cell_spec(k_selection[4,best_k_sil$best_k], bold = T)
k_selection[5,best_k_icl$best_k]<-cell_spec(k_selection[5,best_k_icl$best_k], bold = T)
  
colnames(k_selection)<-c("k = 1", "k = 2", "k = 3", "k = 4", "k = 5")
rownames(k_selection)<-c("AIC criteria", "Log-likelihood criteria","BIC criteria", "Silhouette criteria", "ICL-based criteria")
```

```{r print selection table, echo=FALSE}
kable(k_selection, format = "html", escape = FALSE)%>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

#### GMM for CL distribution [random initialization, bootstrap, ECM algorithm]

```{r gaussian mixure models, echo=F, results='hide',fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
pal <- c("#0099B499","#AA3929")
source("code/gmm_fit.R")
source("code/gmm_plot.R")

# run bootstrap to estimate CI
boot_results <- boot_gmm(dataset)

# Fit GMM and create plots
gmm<- fit_gmm(dataset$cl)
plot_gmm<-create_gmm_plot_display(gmm$summary, gmm$density, gmm$gmm, cohort, boot_results)

plot_gmm_save<-create_gmm_plot_save(gmm$summary, gmm$density, gmm$gmm, cohort, boot_results)
file_savename <- paste0("output/Figure-1C_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
ggsave(plot_gmm_save,filename=file_savename,dpi=600,width=10,height=10,units="cm")

plot_gmm_save<-plot_gmm_save+
  geom_vline(xintercept = gmm$gmm$mu[1]+2*gmm$gmm$sigma[1], color = "black", size = 0.5)+
  geom_rect(aes(xmin=boot_results[[5]]$percent[4],xmax=boot_results[[5]]$percent[5], ymin=-Inf, ymax=Inf), fill="black", alpha=0.1)
file_savename <- paste0("output/Figure-1A_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
ggsave(plot_gmm_save,filename=file_savename,dpi=600,width=10,height=10,units="cm")

plot_gmm_save<-plot_gmm_save+ylim(0,0.05)
file_savename <- paste0("output/Figure-1B_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
ggsave(plot_gmm_save,filename=file_savename,dpi=600,width=10,height=10,units="cm")

print(plot_gmm)

# Plot the posterior distribution function
plot_posterior<-create_ppf_plot(gmm$summary, gmm)
print(plot_posterior)
```

```{r print posterior table, echo=FALSE}
# Print the results of analysis applying different cutoffs to the posterior density function 
double_cutoff_table <- t(data.frame(rbind(gmm$cutoff_double_low,gmm$cutoff_double_high)))
colnames(double_cutoff_table)<-c("Clearly negative cutoff", "Clearly positive cutoff")
rownames(double_cutoff_table)<-c("Posterior probability [cutoff] = 0.50","Posterior probability [cutoff] = 0.60","Posterior probability [cutoff] = 0.70","Posterior probability [cutoff] = 0.80","Posterior probability [cutoff] = 0.90")
kable(double_cutoff_table, format = "html", escape = FALSE)%>%
    kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)
```

```{r gaussian mixure models by tracer, echo=F, results='hide'}
# Initialize a list to store results by radiotracer
gmm_tracer <- list()
boot_results_tracer<-list()

for (tracer_name in unique(dataset$tracer)) {
  if (length(unique(dataset$tracer))>1) {
    # Subset the data for the current tracer
    data <- subset(dataset, dataset$tracer == tracer_name)
    
    # Run bootstrap to estimate CI with error handling
    boot_results_tracer[[tracer_name]] <- tryCatch({boot_gmm(data)}, 
                                                   error = function(e) {
                                                     message(paste("Error in boot_gmm for tracer:", tracer_name, "- Error message:", e$message)) 
                                                     NA})
    
    # Fit GMM and create plots with error handling
    gmm_tracer[[tracer_name]] <- tryCatch({fit_gmm(data$cl)},
                                          error = function(e) {
                                            message(paste("Error in fit_gmm for tracer:", tracer_name, "- Error message:", e$message))
                                            NA})
  } else {
     boot_results_tracer[[tracer_name]]<-boot_results
     gmm_tracer[[tracer_name]]<-gmm
  }
}
```

## Chapter II: Correspondence between quantification and visual read

#### Cutoff based on maximizing kappa: correspondance between visual read and quantification

```{r kappa and VR analysis, echo=F, results='hide', fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
source("code/visual_read_plot.R")
pal2<-c("#0A9F9D","#9986A5")

# extract cutoffs maximizing kappa
if ("visual_read" %in% colnames(dataset)) {
    data<-subset(dataset, is.na(dataset$visual_read)==F)
    cutoff<-cutpointr(data, cl, visual_read, direction = ">=", pos_class = "positive",
                    method = maximize_metric, metric = cohens_kappa, boot_runs=5000)

  # Calculate standard error for the optimal cutpoint
  kappa_calculated<-cutoff$cohens_kappa
  cutoff_max_kappa<-cutoff$optimal_cutpoint
  cutoff_max_kappa_ci<-quantile(cutoff$boot[[1]]$optimal_cutpoint, probs = c(0.025, 0.975))
  kappa_calculated_ci<-quantile(cutoff$boot[[1]]$cohens_kappa_b, probs = c(0.025, 0.975))

  #plot
  vr_plot<-plot_vr(data,cohort,cutoff_max_kappa)
  vr_save<-vr_plot+
    theme(axis.text.x = element_text(size = 16),
          axis.text.y = element_text(size = 16))+
    xlab("")+
    theme(axis.text.y=element_blank())

  file_savename <- paste0("output/Figure-2A_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
  ggsave(vr_save,filename=file_savename,dpi=600,width=10,height=10,units="cm")
  
  #plot
  vr_kappa<-vr_save+
    geom_vline(xintercept = cutoff_max_kappa, linetype = "dotted", color = "black", size = 1)

  file_savename <- paste0("output/Figure-2B_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
  ggsave(vr_kappa,filename=file_savename,dpi=600,width=10,height=10,units="cm")

  vr_plot<-vr_plot+
    annotate("text",x=cutoff_max_kappa+20, y = 2.5, label = paste(round(as.numeric(cutoff_max_kappa),1), "[Kappa = ", round(as.numeric(kappa_calculated),2),"]"), color = "black")+
    geom_vline(xintercept = cutoff_max_kappa, linetype = "dotted", color = "black", size = 1) +
    ggtitle(paste(cohort))
    print(vr_plot)
}
```

```{r kappa and VR analysis by tracer, echo=F, results='hide', fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
# extract kappa-based cutoffs for each tracer
if ("visual_read" %in% colnames(dataset)) {
    vr_tracer <- list()
    for (tracer_name in unique(dataset$tracer)){
        if (length(unique(dataset$tracer)>1)) {
          data<-subset(dataset,dataset$tracer==tracer_name)
          data<-subset(data, is.na(data$visual_read)==F)
          vr_tracer[[tracer_name]]$cutoff<-tryCatch(
            {cutpointr(data, cl, visual_read, direction = ">=",
                pos_class = "positive",method = maximize_metric, metric = cohens_kappa, boot_runs=5000)},
              error = function(e) {
                message(paste("Error in calculate_cutoff for tracer:", tracer_name, "- Error message:", e$message))
                NA}) 
  
          # Calculate standard error for the optimal cutpoint
          vr_tracer[[tracer_name]]$kappa_calculated<-tryCatch(vr_tracer[[tracer_name]]$cutoff$cohens_kappa, error = function(e) NA)
          vr_tracer[[tracer_name]]$cutoff_max_kappa<-tryCatch(vr_tracer[[tracer_name]]$cutoff$optimal_cutpoint, error = function(e) NA)
          vr_tracer[[tracer_name]]$cutoff_max_kappa_ci<-tryCatch(quantile(vr_tracer[[tracer_name]]$cutoff$boot[[1]]$optimal_cutpoint, probs = c(0.025, 0.975)), error = function(e) NA)
          vr_tracer[[tracer_name]]$kappa_calculated_ci<-tryCatch(quantile(vr_tracer[[tracer_name]]$cutoff$boot[[1]]$cohens_kappa_b, probs = c(0.025, 0.975)), error = function(e) NA)

        } else {
          vr_tracer[[tracer_name]]$cutoff<-cutoff
          vr_tracer[[tracer_name]]$kappa_calculated<-kappa_calculated
          vr_tracer[[tracer_name]]$cutoff_max_kappa<-cutoff_max_kappa
          vr_tracer[[tracer_name]]$cutoff_max_kappa_ci<-cutoff_max_kappa_ci
          vr_tracer[[tracer_name]]$kappa_calculated_ci<-kappa_calculated_ci
        }
    }
}
```

#### Cutoff based on ROC AUC analysis with Youden index
```{r roc, echo=F,  results='hide',fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
# Use ROC as an alternative methods to define VR-based cutoffs
source('code/roc_calculate.R')
if ("visual_read" %in% colnames(dataset)) {
    data<-subset(dataset, is.na(dataset$visual_read)==F)
    result_roc<- tryCatch({calculate_cutoff(data)},
                          error = function(e) {
                            message(paste("Error in calculate_cutoff for tracer:", tracer_name, "- Error message:", e$message))
                            NA})

    roc_plot<-create_roc_plot(result_roc$roc_curve, result_roc$cutoff_youden, cohort)

    # add ROC cutoff to VR plot
    vr_save<-vr_save+
      theme(axis.text.x = element_text(size = 16),
        axis.text.y = element_text(size = 16))+
      xlab("")+
      theme(axis.text.y=element_blank())+
      geom_vline(xintercept = result_roc$cutoff_youden$threshold,  linetype = "dotted", color = "black", size = 1)

    file_savename <- paste0("output/Figure-2C_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(vr_save,filename=file_savename,dpi=600,width=10,height=10,units="cm")

    file_savename <- paste0("output/Figure-3_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(roc_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
    print(roc_plot)
}
```

```{r roc by tracer, echo=F,  results='hide'}
# perform the ROC analyses by radiotracer
if ("visual_read" %in% colnames(dataset)) {
    roc_tracer <- list()
    for (tracer_name in unique(dataset$tracer)){
      if (n_distinct(as.factor(dataset$tracer))>1){
        data<-subset(dataset,dataset$tracer==tracer_name)
        data<-subset(data, is.na(data$visual_read)==F)
        roc_tracer[[tracer_name]]$result_roc <- tryCatch({calculate_cutoff(data)},
                                                         error = function(e) {
                                                           message(paste("Error in calculate_cutoff for tracer:", tracer_name, "- Error message:", e$message)) 
                                                           NA})
      }
    }
}
```

## Chapter III: Association with non-imaging data

#### Association with age and sex

```{r basic demog, echo=F, fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
# Centiloid to age association with Pearson correlation test; Centiloid by sex with T-test
source('code/basic_demog_plot.R')
age1<-plot_age(dataset,cohort,'')
file_savename <- paste0("output/Figure-4_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
ggsave(age1$age_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
age1$age_plot<-age1$age_plot+stat_cor(method="pearson", size = 4, show.legend = F)
text_disp <- paste0("Centiloid by age association: Pearson r - ",
                    round(age1$correlation_age_cl$estimate, 3),
                    ", p-value - ",
                    format.pval(age1$correlation_age_cl$p.value, digits = 3),
                    ".\n")

model_age_full<-lm(cl~age, data=dataset)
text_disp <- paste0(text_disp,
                    "Centiloid by age association: intercept -  ",
                    round(model_age_full$coefficients[1], 3),
                    ", slope - ",
                    round(model_age_full$coefficients[2], digits = 3),
                    ", p-value - ",
                    format.pval(summary(model_age_full)$coefficient[2,4], digits = 3),
                    ".\n")

if ("dx" %in% colnames(dataset)) {
  age2<-plot_age(dataset,cohort,dataset$dx)
  if (!is.null(age2$correlation_age_cl$cn)) {
    file_savename <- paste0("output/Figure-4A_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(age2$age_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
    age2$age_plot<-age2$age_plot+stat_cor(method="pearson",size = 4, show.legend = F)
    text_disp <- paste0(text_disp,
                        "Centiloid by age association in CN: Pearson r - ",
                        round(age2$correlation_age_cl$cn$estimate, 3),
                        ", p-value - ",
                        format.pval(age2$correlation_age_cl$cn$p.value, digits = 3),
                        ".\n")
    text_disp <- paste0(text_disp,
                        "Centiloid by age association in Cognitively Impaired: Pearson r - ",
                        round(age2$correlation_age_cl$patient$estimate, 3),
                        ", p-value - ",
                        format.pval(age2$correlation_age_cl$patient$p.value, digits = 3),
                        ".\n")

    model_age_cn<-lm(cl~age, data=subset(dataset,dataset$dx=="CN"))
    text_disp <- paste0(text_disp,
                        "Centiloid by age association in CN: intercept -  ",
                      round(model_age_cn$coefficients[1], 3),
                      ", slope - ",
                      round(model_age_cn$coefficients[2], digits = 3),
                      ", p-value - ",
                      format.pval(summary(model_age_cn)$coefficient[2,4], digits = 3),
                      ".\n")

    model_age_pt<-lm(cl~age, data=subset(dataset,dataset$dx!="CN"))
    text_disp <- paste0(text_disp,
                      "Centiloid by age association in Cognitively Impaired: intercept -  ",
                      round(model_age_pt$coefficients[1], 3),
                      ", slope - ",
                      round(model_age_pt$coefficients[2], digits = 3),
                      ", p-value - ",
                      format.pval(summary(model_age_pt)$coefficient[2,4], digits = 3),
                      ".\n")
  }

} else if ("cdr" %in% colnames(dataset)) {
  age3<-plot_age(dataset,cohort,dataset$cdr)
  if (!is.null(age3$correlation_age_cl$cn)) {
    file_savename <- paste0("output/Figure-4B_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(age3$age_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
    age3$age_plot<-age3$age_plot+stat_cor(method="pearson",size = 4, show.legend = F)
    text_disp <- paste0(text_disp,
                        "Centiloid by age association in CN: Pearson r - ",
                        round(age3$correlation_age_cl$cn$estimate, 3),
                        ", p-value - ",
                        format.pval(age3$correlation_age_cl$cn$p.value, digits = 3),
                        ".\n")
    text_disp <- paste0(text_disp,
                        "Centiloid by age association in Cognitively Impaired: Pearson r - ",
                        round(age3$correlation_age_cl$patient$estimate, 3),
                        ", p-value - ",
                        format.pval(age3$correlation_age_cl$patient$p.value, digits = 3),
                        ".\n")

    model_age_cn<-lm(cl~age, data=subset(dataset,dataset$cdr==0))
    text_disp <- paste0(text_disp,
                      "Centiloid by age association in CN: intercept -  ",
                      round(model_age_cn$coefficients[1], 3),
                      ", slope - ",
                      round(model_age_cn$coefficients[2], digits = 3),
                      ", p-value - ",
                      format.pval(summary(model_age_cn)$coefficient[2,4], digits = 3),
                      ".\n")

    model_age_pt<-lm(cl~age, data=subset(dataset,dataset$cdr!=0))
    text_disp <- paste0(text_disp,
                      "Centiloid by age association in patients: intercept -  ",
                      round(model_age_pt$coefficients[1], 3),
                      ", slope - ",
                      round(model_age_pt$coefficients[2], digits = 3),
                      ", p-value - ",
                      format.pval(summary(model_age_pt)$coefficient[2,4], digits = 3),
                      ".\n")
  }
}

sex1<-plot_sex(dataset,cohort,'')
file_savename <- paste0("output/Figure-5_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
ggsave(sex1$sex_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
sex1$sex_plot<-sex1$sex_plot+stat_compare_means(aes(label = paste0("T-test p = ", after_stat(p.format))),method="t.test")

text_disp <- paste0(text_disp,
                    "Centiloid in males vs. females: T-value - ",
                    round(sex1[["difference_sex_cl"]][["statistic"]][["t"]], 3),
                    ", p-value - ",
                    format.pval(sex1$difference_sex_cl$p.value, digits = 3),
                    ".\n")

if ("dx" %in% colnames(dataset)) {
  sex2<-plot_sex(dataset,cohort,dataset$dx)
  if (!is.null(sex2[["difference_sex_cl"]][["cn"]])) {
    file_savename <- paste0("output/Figure-5A_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(sex2$sex_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
    sex2$sex_plot<-sex2$sex_plot+stat_compare_means(aes(label = paste0("T-test p = ", after_stat(p.format))),method="t.test")
    if (!is.null(sex2[["difference_sex_cl"]][["cn"]][["statistic"]][["t"]])){
      text_disp <- paste0(text_disp,
                        "Centiloid in males vs. females in CN: T-value - ",
                        round(sex2[["difference_sex_cl"]][["cn"]][["statistic"]][["t"]], 3),
                        ", p-value - ",
                        format.pval(sex2$difference_sex_cl$cn$p.value, digits = 3),
                        ".\n")}
    if (!is.null(sex2[["difference_sex_cl"]][["patient"]][["statistic"]][["t"]])){
    text_disp <- paste0(text_disp,
                        "Centiloid in males vs. females in Cognitively Impaired: T-value - ",
                        round(sex2[["difference_sex_cl"]][["patient"]][["statistic"]][["t"]], 3),
                        ", p-value - ",
                        format.pval(sex2$difference_sex_cl$patient$p.value, digits = 3),
                        ".\n")}
  }
} else if ("cdr" %in% colnames(dataset)) {
  sex3<-plot_sex(dataset,cohort,dataset$cdr)
  if (!is.null(sex3[["difference_sex_cl"]][["cn"]])) {
    file_savename <- paste0("output/Figure-5B_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(sex3$sex_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
    sex3$sex_plot<-sex3$sex_plot+stat_compare_means(aes(label = paste0("T-test p = ", after_stat(p.format))),method="t.test")
    if (!is.null(sex3[["difference_sex_cl"]][["cn"]][["statistic"]][["t"]])){
    text_disp <- paste0(text_disp,
                        "Centiloid in males vs. females in CN: T-value - ",
                        round(sex3[["difference_sex_cl"]][["cn"]][["statistic"]][["t"]], 3),
                        ", p-value - ",
                        format.pval(sex3$difference_sex_cl$cn$p.value, digits = 3),
                        ".\n")}
     if (!is.null(sex3[["difference_sex_cl"]][["patient"]][["statistic"]][["t"]])){
    text_disp <- paste0(text_disp,
                        "Centiloid in males vs. females in Cognitively Impaired: T-value - ",
                        round(sex3[["difference_sex_cl"]][["patient"]][["statistic"]][["t"]], 3),
                        ", p-value - ",
                        format.pval(sex3$difference_sex_cl$patient$p.value, digits = 3),
                        ".\n")}
  }
}

if ("dx" %in% colnames(dataset)) {
  grid.arrange(grobs = list(age2$age_plot,sex2$sex_plot), ncol = 2, bottom = textGrob("Dx based on provided clinical diagnosis."))
} else if ("cdr" %in% colnames(dataset)) {
  grid.arrange(grobs = list(age3$age_plot,sex3$sex_plot), ncol = 2, bottom = textGrob("Dx based on CDR-total score (0 vs >=0.5.)"))
} else {
  grid.arrange(grobs = list(age1$age_plot,sex1$sex_plot), ncol = 2)
}

cat(text_disp)
```


#### Association with cognitive scores

```{r cognition, echo=F, fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
# Centiloid to MMSE/CDR association with Pearson correlation test; Centiloid between CDR groups by ANOVA with Tukey HSD for pairwise

source('code/cognition_plot.R')
if ("mmse" %in% colnames(dataset)) {
  mmse<-plot_mmse(dataset)
  file_savename <- paste0("output/Figure-6_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
  ggsave(mmse$mmse_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
  mmse$mmse_plot<-mmse$mmse_plot+stat_cor(method="pearson", size = 4, show.legend = F)
  print(mmse$mmse_plot)

  model_mmse<-lm(cl~mmse, data=dataset)
  text_disp <- paste0("Centiloid by MMSE association: intercept -  ",
                    round(model_mmse$coefficients[1], 3),
                    ", slope - ",
                    round(model_mmse$coefficients[2], digits = 3),
                    ", p-value - ",
                     format.pval(summary(model_mmse)$coefficient[2,4], digits = 3),
                    ".\n\n")
  cat(text_disp)
}

if ("cdr" %in% colnames(dataset)) {
  cdr<-plot_cdr(dataset,cohort)
  file_savename <- paste0("output/Figure-7_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
  ggsave(cdr$cdr_plot,filename=file_savename,dpi=600,width=10,height=10,units="cm")
  cdr$cdr_plot<-cdr$cdr_plot+stat_compare_means(method = "anova", aes(label = paste0("ANOVA p = ", after_stat(p.format))))
  print(cdr$cdr_plot)

  text_disp <- paste0("Centiloid by CDR, Tukey HSD difference [p-value]:\n")
  cat(text_disp)
  print(cdr[["cdr_tukey"]])
}

```

#### Association with APOE E4

```{r apoe, echo=F, fig.keep='all', dpi = 600, fig.retina=1, fig.height=7, fig.width=10}
# Centiloid between APOE groups by ANOVA with Tukey HSD for pairwise

source("code/apoe_stats_plot.R")
source("code/apoe_stats_dx.R")
if ("apoe4_status" %in% colnames(dataset)) {
  if (nrow(subset(dataset,is.na(dataset$apoe4_status)==F))!=0) {
    apoe<-plot_apoe(dataset, cohort)
    file_savename <- paste0("output/Figure-8A_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(apoe$apoe_plot,filename=file_savename,dpi=600,width=12,height=10,units="cm")
    apoe$apoe_plot<-apoe$apoe_plot+
      stat_compare_means(method = "anova", aes(label = paste0("ANOVA p = ", after_stat(p.format))))+
      theme(axis.text.x = element_text(size = 12))
    print(apoe$apoe_plot)

    text_disp <- paste0("Centiloid by APOE4 status, Tukey HSD difference:\n")
    cat(text_disp)
    print(apoe[["apoe_tukey"]][["as.factor(apoe4_status)"]])
  }

    apoe_full<-plot_apoe_full(dataset, cohort)
    file_savename <- paste0("output/Figure-8B_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".jpeg")
    ggsave(apoe_full$apoe_plot,filename=file_savename,dpi=600,width=12,height=10,units="cm")
    apoe_full$apoe_plot<-apoe_full$apoe_plot+stat_compare_means(method = "anova", aes(label = paste0("ANOVA p = ", after_stat(p.format))))
    print(apoe_full$apoe_plot)
    print(apoe_full[["apoe_tukey"]][["as.factor(apoe)"]])

    if ("dx" %in% colnames(dataset)) {
      apoe_stats_dx<-analyze_apoe_dx(dataset, dataset$dx)
    } else if ("cdr" %in% colnames(dataset)) {
      apoe_stats_dx<-analyze_apoe_dx(dataset, dataset$cdr)
    }
  }

```

## Summary

```{r summary metrices, echo =F}
source("metadata/table_list.R")
# Aggregate results in the summary table and save in .csv
for (tracer in unique(dataset$tracer)) {

  #Demographics
  n_tracer[[tracer]] <- length(dataset$id[dataset$tracer == tracer])
  age_tracer[[tracer]] <- mean(dataset$age[dataset$tracer == tracer])
  age_sd_tracer[[tracer]] <- sd(dataset$age[dataset$tracer == tracer])
  male_tracer[[tracer]] <- sum(dataset$male[dataset$tracer == tracer])
  n_vr_tracer[[tracer]] <- sum(!is.na(dataset$visual_read) & dataset$tracer == tracer)

  if ("apoe4_status" %in% colnames(dataset)) {
    n_apoe_tracer[[tracer]] <- sum(dataset$tracer == tracer & is.na(dataset$apoe4_status) == F)
    n_apoe_non_c_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$apoe4_status == 'Non-Carrier' & is.na(dataset$apoe4_status) == F)
    n_apoe_homo_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$apoe4_status == 'Homozygous-Carrier' & is.na(dataset$apoe4_status) == F)
    n_apoe_hetero_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$apoe4_status == 'Heterozygous-Carrier' & is.na(dataset$apoe4_status) == F)
    }

   if ("dx" %in% colnames(dataset)) {
      n_dx_tracer[[tracer]] <- sum(dataset$tracer == tracer & is.na(dataset$dx) == FALSE)
      n_cn_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$dx == "CN" & is.na(dataset$dx) == FALSE)
      n_mci_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$dx == "MCI" & is.na(dataset$dx) == FALSE)
      n_dementia_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$dx == "Dementia" & is.na(dataset$dx) == FALSE) }

    if ("cdr" %in% colnames(dataset)) {
      n_cn_cdr_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$cdr == 0, na.rm=TRUE)
      n_patient_cdr_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$cdr >= 0.5, na.rm=TRUE)
    }

  #Cognition
  if ("cdr" %in% colnames(dataset)) {
    n_cdr_tracer[[tracer]] <- sum(dataset$tracer == tracer & is.na(dataset$cdr) == FALSE)
    cdr_mean_tracer[[tracer]] <- mean(dataset$cdr[dataset$tracer == tracer], na.rm = TRUE)
    cdr_sd_tracer[[tracer]] <- sd(dataset$cdr[dataset$tracer == tracer], na.rm = TRUE)
  }

  if ("mmse" %in% colnames(dataset)) {
    n_mmse_tracer[[tracer]] <- sum(dataset$tracer == tracer & is.na(dataset$mmse) == FALSE)
    mmse_mean_tracer[[tracer]] <- mean(dataset$mmse[dataset$tracer == tracer], na.rm = TRUE)
    mmse_sd_tracer[[tracer]] <- sd(dataset$mmse[dataset$tracer == tracer], na.rm = TRUE)
  }

  #GMM
  gauss1_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$gmm$mu[1], error = function(e) NA)
  gauss1_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[1]]$percent[4], error = function(e) NA)
  gauss1_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[1]]$percent[5], error = function(e) NA)
  gauss2_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$gmm$mu[2], error = function(e) NA)
  gauss2_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[2]]$percent[4], error = function(e) NA)
  gauss2_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[2]]$percent[5], error = function(e) NA)
  gausssd1_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$gmm$sigma[1], error = function(e) NA)
  gausssd1_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[3]]$percent[4], error = function(e) NA)
  gausssd1_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[3]]$percent[5], error = function(e) NA)
  gausssd2_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$gmm$sigma[2], error = function(e) NA)
  gausssd2_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[4]]$percent[4], error = function(e) NA)
  gausssd2_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[4]]$percent[5], error = function(e) NA)
  cutoff_gmm_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$gmm$cutoff, error = function(e) NA)
  cutoff_gmm_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[5]]$percent[4], error = function(e) NA)
  cutoff_gmm_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[5]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_low_0p5_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_low[["0.5"]], error = function(e) NA)
  cutoff_gmm_double_low_0p5_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[6]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_low_0p5_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[6]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_high_0p5_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_high[["0.5"]], error = function(e) NA)
  cutoff_gmm_double_high_0p5_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[7]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_high_0p5_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[7]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_low_0p6_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_low[["0.6"]], error = function(e) NA)
  cutoff_gmm_double_low_0p6_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[8]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_low_0p6_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[8]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_high_0p6_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_high[["0.6"]], error = function(e) NA)
  cutoff_gmm_double_high_0p6_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[9]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_high_0p6_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[9]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_low_0p7_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_low[["0.7"]], error = function(e) NA)
  cutoff_gmm_double_low_0p7_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[10]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_low_0p7_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[10]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_high_0p7_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_high[["0.7"]], error = function(e) NA)
  cutoff_gmm_double_high_0p7_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[11]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_high_0p7_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[11]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_low_0p8_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_low[["0.8"]], error = function(e) NA)
  cutoff_gmm_double_low_0p8_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[12]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_low_0p8_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[12]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_high_0p8_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_high[["0.8"]], error = function(e) NA)
  cutoff_gmm_double_high_0p8_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[13]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_high_0p8_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[13]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_low_0p9_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_low[["0.9"]], error = function(e) NA)
  cutoff_gmm_double_low_0p9_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[14]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_low_0p9_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[14]]$percent[5], error = function(e) NA)
  cutoff_gmm_double_high_0p9_tracer[[tracer]] <- tryCatch(gmm_tracer[[tracer]]$cutoff_double_high[["0.9"]], error = function(e) NA)
  cutoff_gmm_double_high_0p9_tracer_ci_low[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[15]]$percent[4], error = function(e) NA)
  cutoff_gmm_double_high_0p9_tracer_ci_upp[[tracer]] <- tryCatch(boot_results_tracer[[tracer]][[15]]$percent[5], error = function(e) NA)

  #VR
  if ("visual_read" %in% colnames(dataset)) {
    cutoff_kappa_tracer[[tracer]] <- tryCatch(vr_tracer[[tracer]]$cutoff_max_kappa, error = function(e) NA)
    cutoff_kappa_tracer_ci_low[[tracer]] <- tryCatch(vr_tracer[[tracer]]$cutoff_max_kappa_ci[1], error = function(e) NA)
    cutoff_kappa_tracer_ci_upp[[tracer]] <- tryCatch(vr_tracer[[tracer]]$cutoff_max_kappa_ci[2], error = function(e) NA)
    kappa_tracer[[tracer]] <- tryCatch(vr_tracer[[tracer]]$kappa_calculated, error = function(e) NA)
    kappa_tracer_ci_low[[tracer]] <- tryCatch(vr_tracer[[tracer]]$kappa_calculated_ci[1], error = function(e) NA)
    kappa_tracer_ci_upp[[tracer]] <- tryCatch(vr_tracer[[tracer]]$kappa_calculated_ci[2], error = function(e) NA)
    cutoff_youden_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_youden$threshold, error = function(e) NA)
    cutoff_youden_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_youden_ci$threshold[1], error = function(e) NA)
    cutoff_youden_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_youden_ci$threshold[3], error = function(e) NA)
    auc_roc_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$roc_curve$auc[1], error = function(e) NA)
    auc_roc_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$auc_ci[1], error = function(e) NA)
    auc_roc_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$auc_ci[3], error = function(e) NA)
    cutoff_95sens_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95sens, error = function(e) NA)
    cutoff_95sens_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95sens_ci$percent[4], error = function(e) NA)
    cutoff_95sens_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95sens_ci$percent[5], error = function(e) NA)
    cutoff_95spec_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95spec, error = function(e) NA)
    cutoff_95spec_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95spec_ci$percent[4], error = function(e) NA)
    cutoff_95spec_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_95spec_ci$percent[5], error = function(e) NA)
    cutoff_90sens_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90sens, error = function(e) NA)
    cutoff_90sens_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90sens_ci$percent[4], error = function(e) NA)
    cutoff_90sens_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90sens_ci$percent[5], error = function(e) NA)
    cutoff_90spec_tracer[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90spec, error = function(e) NA)
    cutoff_90spec_tracer_ci_low[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90spec_ci$percent[4], error = function(e) NA)
    cutoff_90spec_tracer_ci_upp[[tracer]] <- tryCatch(roc_tracer[[tracer]]$result_roc$cutoff_90spec_ci$percent[5], error = function(e) NA)
    n_vr_positive_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$visual_read == 'positive', na.rm = TRUE)
    n_vr_negative_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$visual_read == 'negative', na.rm = TRUE)
  }


  #CL raw
  cl_male_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$male == 1], na.rm = TRUE)
  cl_female_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$male == 0], na.rm = TRUE)
  cl_sd_male_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$male == 1], na.rm = TRUE)
  cl_sd_female_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$male == 0], na.rm = TRUE)

  if ("apoe4_status" %in% colnames(dataset)) {
    cl_apoe_non_c_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Non-Carrier'], na.rm = TRUE)
    cl_sd_apoe_non_c_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Non-Carrier'], na.rm = TRUE)
    cl_apoe_homo_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Homozygous-Carrier'], na.rm = TRUE)
    cl_sd_apoe_homo_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Homozygous-Carrier'], na.rm = TRUE)
    cl_apoe_hetero_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Heterozygous-Carrier'], na.rm = TRUE)
    cl_sd_apoe_hetero_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$apoe4_status == 'Heterozygous-Carrier'], na.rm = TRUE)
  }
  if ("visual_read" %in% colnames(dataset)) {
    cl_vr_positive_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$visual_read == 'positive'], na.rm = TRUE)
    cl_sd_vr_positive_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$visual_read == 'positive'], na.rm = TRUE)
    cl_vr_negative_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$visual_read == 'negative'], na.rm = TRUE)
    cl_sd_vr_negative_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$visual_read == 'negative'], na.rm = TRUE)
  }
  if ("cdr" %in% colnames(dataset)) {
    cl_cdr_0_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$cdr == 0], na.rm = TRUE)
    cl_cdr_0p5_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$cdr == 0.5], na.rm = TRUE)
    cl_cdr_more1_tracer[[tracer]] <- mean(dataset$cl[dataset$tracer == tracer & dataset$cdr >= 1], na.rm = TRUE)

    cl_sd_cdr_0_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$cdr == 0], na.rm = TRUE)
    cl_sd_cdr_0p5_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$cdr == 0.5], na.rm = TRUE)
    cl_sd_cdr_more1_tracer[[tracer]] <- sd(dataset$cl[dataset$tracer == tracer & dataset$cdr >= 1], na.rm = TRUE)

    cl_n_cdr_0_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$cdr == 0, na.rm = TRUE)
    cl_n_cdr_0p5_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$cdr == 0.5, na.rm = TRUE)
    cl_n_cdr_more1_tracer[[tracer]] <- sum(dataset$tracer == tracer & dataset$cdr >= 1, na.rm = TRUE)
  }
}


Stats <- data.frame(
  # Full cohort and unique tracers as columns
  columns = c("Full Cohort", unique(dataset$tracer)),

  # Demographics
  n = c(length(dataset$id), unlist(n_tracer, use.names = FALSE)),
  age_mean = c(mean(dataset$age), unlist(age_tracer, use.names = FALSE)),
  age_sd = c(sd(dataset$age), unlist(age_sd_tracer, use.names = FALSE)),
  male = c(sum(dataset$male), unlist(male_tracer, use.names = FALSE)),
  vr_n = c(sum(!is.na(dataset$visual_read)), unlist(n_vr_tracer, use.names = FALSE)),
  n_cu = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$group_counts[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$group_counts[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  n_ci = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$group_counts[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$group_counts[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  n_cu_male = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$n_male[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$n_male[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  n_cu_female = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$n_female[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$n_female[['cn']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  n_ci_male = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$n_male[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$n_male[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  n_ci_female = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(sex2$n_female[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(sex3$n_female[['patient']], rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  

  # APOE4 status (if exists)
  n_apoe = if ("apoe4_status" %in% colnames(dataset)) {
    c(sum(!is.na(dataset$apoe4_status)), unlist(n_apoe_tracer, use.names = FALSE))
  } else NA,
  n_apoe_non_c = if ("apoe4_status" %in% colnames(dataset)) {
    c(sum(dataset$apoe4_status == "Non-Carrier", na.rm = TRUE), unlist(n_apoe_non_c_tracer, use.names = FALSE))
  } else NA,
  n_apoe_homo = if ("apoe4_status" %in% colnames(dataset)) {
    c(sum(dataset$apoe4_status == "Homozygous-Carrier", na.rm = TRUE), unlist(n_apoe_homo_tracer, use.names = FALSE))
  } else NA,
  n_apoe_hetero = if ("apoe4_status" %in% colnames(dataset)) {
    c(sum(dataset$apoe4_status == "Heterozygous-Carrier", na.rm = TRUE), unlist(n_apoe_hetero_tracer, use.names = FALSE))
  } else NA,
  
  n_apoe_non_cn = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_non_n[["cn"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  n_apoe_homo_cn = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_homo_n[["cn"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  n_apoe_hetero_cn = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_hetero_n[["cn"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  n_apoe_non_pt = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_non_n[["patient"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  n_apoe_homo_pt = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_homo_n[["patient"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  n_apoe_hetero_pt = if ("apoe4_status" %in% colnames(dataset)) {
    c(apoe_stats_dx$apoe_hetero_n[["patient"]], rep("-", length(unique(dataset$tracer))))
  } else NA,
  

  # Diagnosis (if exists)
  n_dx = if ("dx" %in% colnames(dataset)) {
    c(sum(!is.na(dataset$dx)), unlist(n_dx_tracer, use.names = FALSE))
  } else NA,
  n_cn = if ("dx" %in% colnames(dataset)) {
    c(sum(dataset$dx == "CN", na.rm = TRUE), unlist(n_cn_tracer, use.names = FALSE))
  } else NA,
  n_mci = if ("dx" %in% colnames(dataset)) {
    c(sum(dataset$dx == "MCI", na.rm = TRUE), unlist(n_mci_tracer, use.names = FALSE))
  } else NA,
  n_dementia = if ("dx" %in% colnames(dataset)) {
    c(sum(dataset$dx == "Dementia", na.rm = TRUE), unlist(n_dementia_tracer, use.names = FALSE))
  } else NA,

  # CDR categories (if exists)
  n_cdr = if ("cdr" %in% colnames(dataset)) {
    c(sum(!is.na(dataset$cdr)), unlist(n_cdr_tracer, use.names = FALSE))
  } else NA,
  n_cn_cdr = if ("cdr" %in% colnames(dataset)) {
    c(sum(dataset$cdr == 0, na.rm = TRUE), unlist(n_cn_cdr_tracer, use.names = FALSE))
  } else NA,
  n_patient_cdr = if ("cdr" %in% colnames(dataset)) {
    c(sum(dataset$cdr >= 0.5, na.rm = TRUE), unlist(n_patient_cdr_tracer, use.names = FALSE))
  } else NA,

  # Cognition measures (if exists)

  cdr_mean = if ("cdr" %in% colnames(dataset)) {
    c(mean(dataset$cdr, na.rm = TRUE), unlist(cdr_mean_tracer, use.names = FALSE))
  } else NA,
  cdr_sd = if ("cdr" %in% colnames(dataset)) {
    c(sd(dataset$cdr, na.rm = TRUE), unlist(cdr_sd_tracer, use.names = FALSE))
  } else NA,

  # MMSE measures (if exists)
  n_mmse = if ("mmse" %in% colnames(dataset)) {
    c(sum(!is.na(dataset$mmse)), unlist(n_mmse_tracer, use.names = FALSE))
  } else NA,
  mmse_mean = if ("mmse" %in% colnames(dataset)) {
    c(mean(dataset$mmse, na.rm = TRUE), unlist(mmse_mean_tracer, use.names = FALSE))
  } else NA,
  mmse_sd = if ("mmse" %in% colnames(dataset)) {
    c(sd(dataset$mmse, na.rm = TRUE), unlist(mmse_sd_tracer, use.names = FALSE))
  } else NA,

  # GMM parameters
  gauss1=c(gmm$gmm$mu[1], unlist(gauss1_tracer,use.names=FALSE)),
  gauss1_ci_low = c(boot_results[[1]]$percent[4], unlist(gauss1_tracer_ci_low, use.names = FALSE)),
  gauss1_ci_upp = c(boot_results[[1]]$percent[5], unlist(gauss1_tracer_ci_upp, use.names = FALSE)),
  gauss2 = c(gmm$gmm$mu[2], unlist(gauss2_tracer, use.names = FALSE)),
  gauss2_ci_low = c(boot_results[[2]]$percent[4], unlist(gauss2_tracer_ci_low, use.names = FALSE)),
  gauss2_ci_upp = c(boot_results[[2]]$percent[5], unlist(gauss2_tracer_ci_upp, use.names = FALSE)),
  gausssd1 = c(gmm$gmm$sigma[1], unlist(gausssd1_tracer, use.names = FALSE)),
  gausssd1_ci_low = c(boot_results[[3]]$percent[4], unlist(gausssd1_tracer_ci_low, use.names = FALSE)),
  gausssd1_ci_upp = c(boot_results[[3]]$percent[5], unlist(gausssd1_tracer_ci_upp, use.names = FALSE)),
  gausssd2 = c(gmm$gmm$sigma[2], unlist(gausssd2_tracer, use.names = FALSE)),
  gausssd2_ci_low = c(boot_results[[4]]$percent[4], unlist(gausssd2_tracer_ci_low, use.names = FALSE)),
  gausssd2_ci_upp = c(boot_results[[4]]$percent[5], unlist(gausssd2_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm = c(gmm$gmm$cutoff, unlist(cutoff_gmm_tracer, use.names = FALSE)),
  cutoff_gmm_ci_low = c(boot_results[[5]]$percent[4], unlist(cutoff_gmm_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_ci_upp = c(boot_results[[5]]$percent[5], unlist(cutoff_gmm_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_low_0p5 = c(gmm$cutoff_double_low[["0.5"]], unlist(cutoff_gmm_double_low_0p5_tracer, use.names = FALSE)),
  cutoff_gmm_double_low_0p5_ci_low = c(boot_results[[6]]$percent[4], unlist(cutoff_gmm_double_low_0p5_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_low_0p5_ci_upp = c(boot_results[[6]]$percent[5], unlist(cutoff_gmm_double_low_0p5_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_high_0p5 = c(gmm$cutoff_double_high[["0.5"]], unlist(cutoff_gmm_double_high_0p5_tracer, use.names = FALSE)),
  cutoff_gmm_double_high_0p5_ci_low = c(boot_results[[7]]$percent[4], unlist(cutoff_gmm_double_high_0p5_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_high_0p5_ci_upp = c(boot_results[[7]]$percent[5], unlist(cutoff_gmm_double_high_0p5_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_low_0p6 = c(gmm$cutoff_double_low[["0.6"]], unlist(cutoff_gmm_double_low_0p6_tracer, use.names = FALSE)),
  cutoff_gmm_double_low_0p6_ci_low = c(boot_results[[8]]$percent[4], unlist(cutoff_gmm_double_low_0p6_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_low_0p6_ci_upp = c(boot_results[[8]]$percent[5], unlist(cutoff_gmm_double_low_0p6_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_high_0p6 = c(gmm$cutoff_double_high[["0.6"]], unlist(cutoff_gmm_double_high_0p6_tracer, use.names = FALSE)),
  cutoff_gmm_double_high_0p6_ci_low = c(boot_results[[9]]$percent[4], unlist(cutoff_gmm_double_high_0p6_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_high_0p6_ci_upp = c(boot_results[[9]]$percent[5], unlist(cutoff_gmm_double_high_0p6_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_low_0p7 = c(gmm$cutoff_double_low[["0.7"]], unlist(cutoff_gmm_double_low_0p7_tracer, use.names = FALSE)),
  cutoff_gmm_double_low_0p7_ci_low = c(boot_results[[10]]$percent[4], unlist(cutoff_gmm_double_low_0p7_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_low_0p7_ci_upp = c(boot_results[[10]]$percent[5], unlist(cutoff_gmm_double_low_0p7_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_high_0p7 = c(gmm$cutoff_double_high[["0.7"]], unlist(cutoff_gmm_double_high_0p7_tracer, use.names = FALSE)),
  cutoff_gmm_double_high_0p7_ci_low = c(boot_results[[11]]$percent[4], unlist(cutoff_gmm_double_high_0p7_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_high_0p7_ci_upp = c(boot_results[[11]]$percent[5], unlist(cutoff_gmm_double_high_0p7_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_low_0p8 = c(gmm$cutoff_double_low[["0.8"]], unlist(cutoff_gmm_double_low_0p8_tracer, use.names = FALSE)),
  cutoff_gmm_double_low_0p8_ci_low = c(boot_results[[12]]$percent[4], unlist(cutoff_gmm_double_low_0p8_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_low_0p8_ci_upp = c(boot_results[[12]]$percent[5], unlist(cutoff_gmm_double_low_0p8_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_high_0p8 = c(gmm$cutoff_double_high[["0.8"]], unlist(cutoff_gmm_double_high_0p8_tracer, use.names = FALSE)),
  cutoff_gmm_double_high_0p8_ci_low = c(boot_results[[13]]$percent[4], unlist(cutoff_gmm_double_high_0p8_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_high_0p8_ci_upp = c(boot_results[[13]]$percent[5], unlist(cutoff_gmm_double_high_0p8_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_low_0p9 = c(gmm$cutoff_double_low[["0.9"]], unlist(cutoff_gmm_double_low_0p9_tracer, use.names = FALSE)),
  cutoff_gmm_double_low_0p9_ci_low = c(boot_results[[14]]$percent[4], unlist(cutoff_gmm_double_low_0p9_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_low_0p9_ci_upp = c(boot_results[[14]]$percent[5], unlist(cutoff_gmm_double_low_0p9_tracer_ci_upp, use.names = FALSE)),
  cutoff_gmm_double_high_0p9 = c(gmm$cutoff_double_high[["0.9"]], unlist(cutoff_gmm_double_high_0p9_tracer, use.names = FALSE)),
  cutoff_gmm_double_high_0p9_ci_low = c(boot_results[[15]]$percent[4], unlist(cutoff_gmm_double_high_0p9_tracer_ci_low, use.names = FALSE)),
  cutoff_gmm_double_high_0p9_ci_upp = c(boot_results[[15]]$percent[5], unlist(cutoff_gmm_double_high_0p9_tracer_ci_upp, use.names = FALSE)),

  # VR parameters (if exists)
  cutoff_kappa = if ("visual_read" %in% colnames(dataset)) {
    c(cutoff$optimal_cutpoint, unlist(cutoff_kappa_tracer, use.names = FALSE))
  } else NA,
  cutoff_kappa_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(cutoff_max_kappa_ci[1], unlist(cutoff_kappa_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_kappa_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(cutoff_max_kappa_ci[2], unlist(cutoff_kappa_tracer_ci_upp, use.names = FALSE))
  } else NA,
  kappa = if ("visual_read" %in% colnames(dataset)) {
    c(cutoff$cohens_kappa,unlist(kappa_tracer, use.names = FALSE))
  } else NA,
  kappa_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(kappa_calculated_ci[1],unlist(kappa_tracer_ci_low, use.names = FALSE))
  } else NA,
  kappa_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(kappa_calculated_ci[2],unlist(kappa_tracer_ci_upp, use.names = FALSE))
  } else NA,

  cutoff_youden = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_youden$threshold,unlist(cutoff_youden_tracer, use.names = FALSE))
  } else NA,
  cutoff_youden_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_youden_ci$threshold[1],unlist(cutoff_youden_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_youden_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_youden_ci$threshold[3],unlist(cutoff_youden_tracer_ci_upp, use.names = FALSE))
  } else NA,
  
  auc_roc = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$roc_curve$auc[1],unlist(auc_roc_tracer, use.names = FALSE))
  } else NA,
  auc_roc_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$auc_ci[1],unlist(auc_roc_tracer_ci_low, use.names = FALSE))
  } else NA,
  auc_roc_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$auc_ci[3],unlist(auc_roc_tracer_ci_upp, use.names = FALSE))
  } else NA,
  

  cutoff_95sens = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95sens,unlist(cutoff_95sens_tracer, use.names = FALSE))
  } else NA,
  cutoff_95sens_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95sens_ci$percent[4],unlist(cutoff_95sens_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_95sens_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95sens_ci$percent[5],unlist(cutoff_95sens_tracer_ci_upp, use.names = FALSE))
  } else NA,

  cutoff_95spec = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95spec,unlist(cutoff_95spec_tracer, use.names = FALSE))
  } else NA,
  cutoff_95spec_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95spec_ci$percent[4],unlist(cutoff_95spec_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_95spec_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_95spec_ci$percent[5],unlist(cutoff_95spec_tracer_ci_upp, use.names = FALSE))
  } else NA,
  
  cutoff_90sens = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90sens,unlist(cutoff_90sens_tracer, use.names = FALSE))
  } else NA,
  cutoff_90sens_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90sens_ci$percent[4],unlist(cutoff_90sens_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_90sens_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90sens_ci$percent[5],unlist(cutoff_90sens_tracer_ci_upp, use.names = FALSE))
  } else NA,

  cutoff_90spec = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90spec,unlist(cutoff_90spec_tracer, use.names = FALSE))
  } else NA,
  cutoff_90spec_ci_low = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90spec_ci$percent[4],unlist(cutoff_90spec_tracer_ci_low, use.names = FALSE))
  } else NA,
  cutoff_90spec_ci_upp = if ("visual_read" %in% colnames(dataset)) {
    c(result_roc$cutoff_90spec_ci$percent[5],unlist(cutoff_90spec_tracer_ci_upp, use.names = FALSE))
  } else NA,

  n_vr_positive = if ("visual_read" %in% colnames(dataset)) {
    c(sum(dataset$visual_read=="positive", na.rm=TRUE),unlist(n_vr_positive_tracer, use.names = FALSE))
  } else NA,
  n_vr_negative = if ("visual_read" %in% colnames(dataset)) {
    c(sum(dataset$visual_read=="negative", na.rm=TRUE),unlist(n_vr_negative_tracer, use.names = FALSE))
  } else NA,

  # CL in groups
  cl_male_mean = c(mean(dataset$cl[dataset$male == 1], na.rm = TRUE), unlist(cl_male_tracer, use.names = FALSE)),
  cl_female_mean = c(mean(dataset$cl[dataset$male == 0], na.rm = TRUE), unlist(cl_female_tracer, use.names = FALSE)),
  cl_male_sd = c(sd(dataset$cl[dataset$male == 1], na.rm = TRUE), unlist(cl_sd_male_tracer, use.names = FALSE)),
  cl_female_sd = c(sd(dataset$cl[dataset$male == 0], na.rm = TRUE), unlist(cl_sd_female_tracer, use.names = FALSE)),
  
  cl_cu_male_mean = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$mean_cl_male$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$mean_cl_male$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_cu_female_mean = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$mean_cl_female$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$mean_cl_female$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_cu_male_sd = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$sd_cl_male$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$sd_cl_male$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_cu_female_sd = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$sd_cl_female$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$sd_cl_female$cn[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_ci_male_mean = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$mean_cl_male$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$mean_cl_male$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_ci_female_mean = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$mean_cl_female$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$mean_cl_female$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_ci_male_sd = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$sd_cl_male$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$sd_cl_male$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_ci_female_sd = if (exists("sex2", envir = globalenv())) {
    tryCatch(c(round(sex2$sd_cl_female$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("sex3", envir = globalenv())) {
    tryCatch(c(round(sex3$sd_cl_female$patient[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,

  cl_apoe_non_c_mean = if ("apoe4_status" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$apoe4_status == 'Non-Carrier'], na.rm = TRUE), unlist(cl_apoe_non_c_tracer))
  } else NA,
  cl_apoe_non_c_sd = if ("apoe4_status" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$apoe4_status == 'Non-Carrier'], na.rm = TRUE), unlist(cl_sd_apoe_non_c_tracer))
  } else NA,
  cl_apoe_homo_mean = if ("apoe4_status" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$apoe4_status == 'Homozygous-Carrier'], na.rm = TRUE), unlist(cl_apoe_homo_tracer))
  } else NA,
  cl_apoe_homo_sd = if ("apoe4_status" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$apoe4_status == 'Homozygous-Carrier'], na.rm = TRUE), unlist(cl_sd_apoe_homo_tracer))
  } else NA,
  cl_apoe_hetero_mean = if ("apoe4_status" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$apoe4_status == 'Heterozygous-Carrier'], na.rm = TRUE), unlist(cl_apoe_hetero_tracer))
  } else NA,
  cl_apoe_hetero_sd = if ("apoe4_status" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$apoe4_status == 'Heterozygous-Carrier'], na.rm = TRUE), unlist(cl_sd_apoe_hetero_tracer))
  } else NA,
  
  cl_apoe_cn_non_c_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_non_mean_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_cn_non_c_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_non_sd_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_cn_homo_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_homo_mean_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_cn_homo_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_homo_sd_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_cn_hetero_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_hetero_mean_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_cn_hetero_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_hetero_sd_cl[["cn"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  cl_apoe_pt_non_c_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_non_mean_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_pt_non_c_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_non_sd_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_pt_homo_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_homo_mean_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_pt_homo_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_homo_sd_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_pt_hetero_mean = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_hetero_mean_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  cl_apoe_pt_hetero_sd = if ("apoe4_status" %in% colnames(dataset)) {
    tryCatch(c(round(apoe_stats_dx$apoe_hetero_sd_cl[["patient"]],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,

  cl_vr_positive_mean = if ("visual_read" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$visual_read == 'positive'], na.rm = TRUE), unlist(cl_vr_positive_tracer))
  } else NA,
  cl_vr_positive_sd = if ("visual_read" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$visual_read == 'positive'], na.rm = TRUE), unlist(cl_sd_vr_positive_tracer))
  } else NA,
  cl_vr_negative_mean = if ("visual_read" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$visual_read == 'negative'], na.rm = TRUE), unlist(cl_vr_negative_tracer))
  } else NA,
  cl_vr_negative_sd = if ("visual_read" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$visual_read == 'negative'], na.rm = TRUE), unlist(cl_sd_vr_negative_tracer))
  } else NA,

  cl_n_cdr_0 = if ("cdr" %in% colnames(dataset)) {
    c(sum(dataset$cdr == 0, na.rm = TRUE), unlist(cl_n_cdr_0_tracer))
  } else NA,
  cl_n_cdr_0p5 = if ("cdr" %in% colnames(dataset)) {
    c(sum(dataset$cdr == 0.5, na.rm = TRUE), unlist(cl_n_cdr_0p5_tracer))
  } else NA,
  cl_n_cdr_more1 = if ("cdr" %in% colnames(dataset)) {
    c(sum(dataset$cdr >= 1, na.rm = TRUE), unlist(cl_n_cdr_more1_tracer))
  } else NA,


  cl_cdr_0_mean = if ("cdr" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$cdr == 0], na.rm = TRUE), unlist(cl_cdr_0_tracer))
  } else NA,
  cl_cdr_0p5_mean = if ("cdr" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$cdr == 0.5], na.rm = TRUE), unlist(cl_cdr_0p5_tracer))
  } else NA,
  cl_cdr_more1_mean = if ("cdr" %in% colnames(dataset)) {
    c(mean(dataset$cl[dataset$cdr >= 1], na.rm = TRUE), unlist(cl_cdr_more1_tracer))
  } else NA,

  cl_cdr_0_sd = if ("cdr" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$cdr == 0], na.rm = TRUE), unlist(cl_sd_cdr_0_tracer))
  } else NA,
  cl_cdr_0p5_sd = if ("cdr" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$cdr == 0.5], na.rm = TRUE), unlist(cl_sd_cdr_0p5_tracer))
  } else NA,
  cl_cdr_more1_sd = if ("cdr" %in% colnames(dataset)) {
    c(sd(dataset$cl[dataset$cdr >= 1], na.rm = TRUE), unlist(cl_sd_cdr_more1_tracer))
  } else NA,
  
  # Correlations
  
  r_age_cl = c(tryCatch(round(age1$correlation_age_cl$estimate[1],2), error = function(e) NA), rep("-", length(unique(dataset$tracer)))),
  p_age_cl = c(tryCatch(round(age1$correlation_age_cl$p.value[1],2), error = function(e) NA), rep("-", length(unique(dataset$tracer)))),
  
  r_age_cl_cu = if (exists("age2", envir = globalenv())) {
    tryCatch(c(round(age2$correlation_age_cl$cn$estimate[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("age3", envir = globalenv())) {
    tryCatch(c(round(age3$correlation_age_cl$cn$estimate[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  p_age_cl_cu = if (exists("age2", envir = globalenv())) {
    tryCatch(c(round(age2$correlation_age_cl$cn$p.value[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("age3", envir = globalenv())) {
    tryCatch(c(round(age3$correlation_age_cl$cn$p.value[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  r_age_cl_ci = if (exists("age2", envir = globalenv())) {
    tryCatch(c(round(age2$correlation_age_cl$patient$estimate[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("age3", envir = globalenv())) {
    tryCatch(c(round(age3$correlation_age_cl$patient$estimate[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  p_age_cl_ci = if (exists("age2", envir = globalenv())) {
    tryCatch(c(round(age2$correlation_age_cl$patient$p.value[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else if (exists("age3", envir = globalenv())) {
    tryCatch(c(round(age3$correlation_age_cl$patient$p.value[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  
  r_mmse_cl = if (exists("mmse", envir = globalenv())) {
    tryCatch(c(round(mmse$correlation_mmse_cl$estimate[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA,
  p_mmse_cl = if (exists("mmse", envir = globalenv())) {
    tryCatch(c(round(mmse$correlation_mmse_cl$p.value[1],2), rep("-", length(unique(dataset$tracer)))), error = function(e) NA)
  } else NA)


colnames(Stats)<-c("-", "N","Age (mean, y)","Age (SD, y)","Sex (N male)", "Available visual read (N)",
                   "Cognitively unimpaired (N)", "Cognitively impaired (N)", "Cognitively unimpaired male (N)", "Cognitively unimpaired female (N)",
                   "Cognitively impaired male (N)", "Cognitively impaired female (N)", "Available APOE (N)",
                   "APOE4 Non-Carriers (N)", "APOE4 Homozygous Carriers (N)", "APOE4 Heterozygous Carriers (N)",
                   "APOE4 CU Non-Carriers (N)", "APOE4 CU Homozygous Carriers (N)", "APOE4 CU Heterozygous Carriers (N)",
                   "APOE4 CI Non-Carriers (N)", "APOE4 CI Homozygous Carriers (N)", "APOE4 CI Heterozygous Carriers (N)",
                   "Available Dx (N)","Controls (N)", "MCI (N)", "Dementia (N)", "Available CDR (N)", "Controls (CDR = 0, N)",
                   "Patient (CDR >= 0.5, N)", "CDR (mean)", "CDR (SD)", "Available MMSE (N)", "MMSE (mean)",
                   "MMSE (SD)", "G1 mean (CL)", "G1 mean 95%CI lower bound (CL)", "G1 mean 95%CI upper bound (CL)",
                   "G2 mean (CL)", "G2 mean 95%CI lower bound (CL)", "G2 mean 95%CI upper bound (CL)", "G1 SD (CL)",
                   "G1 SD 95%CI lower bound (CL)", "G1 SD 95%CI upper bound (CL)", "G2 SD (CL)", "G2 SD 95%CI lower bound (CL)",
                   "G2 SD 95%CI upper bound (CL)", "GMM Cutoff (CL)", "GMM Cutoff 95%CI lower bound (CL)",
                   "GMM Cutoff 95%CI upper bound (CL)", "GMM Cutoff Clearly Negative P=0.50 (CL)", "GMM Cutoff Clearly Negative P=0.50 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Negative P=0.50 95%CI upper bound (CL)","GMM Cutoff Clearly Positive P=0.50 (CL)", "GMM Cutoff Clearly Positive P=0.50 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Positive P=0.50 95%CI upper bound (CL)","GMM Cutoff Clearly Negative P=0.60 (CL)", "GMM Cutoff Clearly Negative P=0.60 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Negative P=0.60 95%CI upper bound (CL)","GMM Cutoff Clearly Positive P=0.60 (CL)", "GMM Cutoff Clearly Positive P=0.60 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Positive P=0.60 95%CI upper bound (CL)","GMM Cutoff Clearly Negative P=0.70 (CL)", "GMM Cutoff Clearly Negative P=0.70 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Negative P=0.70 95%CI upper bound (CL)","GMM Cutoff Clearly Positive P=0.70 (CL)", "GMM Cutoff Clearly Positive P=0.70 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Positive P=0.70 95%CI upper bound (CL)","GMM Cutoff Clearly Negative P=0.80 (CL)", "GMM Cutoff Clearly Negative P=0.80 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Negative P=0.80 95%CI upper bound (CL)","GMM Cutoff Clearly Positive P=0.80 (CL)", "GMM Cutoff Clearly Positive P=0.80 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Positive P=0.80 95%CI upper bound (CL)","GMM Cutoff Clearly Negative P=0.90 (CL)", "GMM Cutoff Clearly Negative P=0.90 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Negative P=0.90 95%CI upper bound (CL)","GMM Cutoff Clearly Positive P=0.90 (CL)", "GMM Cutoff Clearly Positive P=0.90 95%CI lower bound (CL)",
                   "GMM Cutoff Clearly Positive P=0.90 95%CI upper bound (CL)",
                   "Kappa-based Cutoff (CL)", "Kappa-based Cutoff 95%CI lower bound (CL)",
                   "Kappa-based Cutoff 95%CI upper bound (CL)", "Max Kappa", "Max Kappa 95%CI lower bound",
                   "Max Kappa 95%CI upper bound", "ROC-based Cutoff [Youden] (CL)",
                   "ROC-based Cutoff [Youden] 95%CI lower bound (CL)", "ROC-based Cutoff [Youden] 95%CI upper bound (CL)",
                   "ROC-based AUC", "ROC-based AUC 95% CI lower bound", "ROC-based AUC 95% CI upper bound",
                   "ROC-based Cutoff [95%-sens] (CL)", "ROC-based Cutoff [95%-sens] 95%CI lower bound (CL)",
                   "ROC-based Cutoff [95%-sens] 95%CI upper bound (CL)","ROC-based Cutoff [95%-spec] (CL)",
                   "ROC-based Cutoff [95%-spec] 95%CI lower bound (CL)","ROC-based Cutoff [95%-spec] 95%CI upper bound (CL)",
                   "ROC-based Cutoff [90%-sens] (CL)", "ROC-based Cutoff [90%-sens] 95%CI lower bound (CL)",
                   "ROC-based Cutoff [90%-sens] 95%CI upper bound (CL)","ROC-based Cutoff [90%-spec] (CL)",
                   "ROC-based Cutoff [90%-spec] 95%CI lower bound (CL)","ROC-based Cutoff [90%-spec] 95%CI upper bound (CL)",
                   "Positive visual read (N)", "Negative visual read (N)", "CL in males (mean)", "CL in females (mean)",
                   "CL in males (SD)", "CL in females (SD)", "CL in CU males (mean)", "CL in CU females (mean)",
                   "CL in CU males (SD)", "CL in CU females (SD)", "CL in CI males (mean)", "CL in CI females (mean)",
                   "CL in CI males (SD)", "CL in CI females (SD)","CL in APOE4 Non-Carriers (mean)", "CL in APOE4 Non-Carriers (SD)",
                   "CL in APOE4 Homozygous Carriers (mean)", "CL in APOE4 Homozygous Carriers (SD)",
                   "CL in APOE4 Heterozygous Carriers (mean)", "CL in APOE4 Heterozygous Carriers (SD)",
                   "CL in CU APOE4 Non-Carriers (mean)", "CL in CU APOE4 Non-Carriers (SD)",
                   "CL in CU APOE4 Homozygous Carriers (mean)", "CL in CU APOE4 Homozygous Carriers (SD)",
                   "CL in CU APOE4 Heterozygous Carriers (mean)", "CL in CU APOE4 Heterozygous Carriers (SD)",
                   "CL in CI APOE4 Non-Carriers (mean)", "CL in CI APOE4 Non-Carriers (SD)",
                   "CL in CI APOE4 Homozygous Carriers (mean)", "CL in CI APOE4 Homozygous Carriers (SD)",
                   "CL in CI APOE4 Heterozygous Carriers (mean)", "CL in CI APOE4 Heterozygous Carriers (SD)",
                   "CL in positive visual read (mean)", "CL in positive visual read (SD)", "CL in negative visual read (mean)",
                   "CL in negative visual read (SD)", "CDR=0 (N)", "CDR=0.5 (N)", "CDR>=1 (N)",
                   "CL in CDR=0 (mean)", "CL in CDR=0.5 (mean)", "CL in CDR>=1 (mean)", "CL in CDR=0 (SD)",
                   "CL in CDR=0.5 (SD)", "CL in CDR>=1 (SD)", "Correlation age-CL (rho)", "Correlation age-CL (p-value)", "Correlation age-CL in CU (rho)", 
                   "Correlation age-CL in CU (p-value)", "Correlation age-CL in CI (rho)", "Correlation age-CL in CI (p-value)",
                   "Correlation MMSE-CL (rho)", "Correlation MMSE-CL (p-value)")
rownames(Stats) <- NULL
Stats%>%
  mutate(across(where(is.numeric), ~ round(., digits = 2))) %>%
  t()%>%
  kable(format = "html")%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = T)%>%
  pack_rows("Cohort Description", 2, 12)%>%
  pack_rows("Genetic Data", 13, 22)%>%
  pack_rows("Clinical Data", 23, 34)%>%
  pack_rows("GMM Results", 35, 79)%>%
  pack_rows("Correspondence to Visual Read", 80, 105)%>%
  pack_rows("Quantification by feature", 106, 148)%>%
  pack_rows("Associations", 149, 156)%>%
  row_spec(1, bold=T)

file_savename <- paste0("output/Table_summary_", cohort, "_", format(Sys.Date(), "%Y-%m-%d"), ".csv")
write.csv(Stats,file_savename, row.names = T)
```

This report was generated on `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`.
Code created by Ganna Blazhenets; ganna.blazhenets @ ucsf.edu.
